Chapter 2 Figures

### 2019-12-31 doc/figureFiles/figures.Rmd
wraped up Bret's suggestions for figure

@@

First run of the vertica facets looks awful and squished. fix it.

```{r strain.table.plot.v2, echo=FALSE, warning=FALSE}
#use the MLH1 / cell level data to calq the error bars
#strain table ggplot
#remove facet by sex

Fig1_Bv2_strain <- ggplot(strain.table.HQ, aes(y=mean_co, x=strain, color=strain, shape = sex))+
  #facet_grid(~sex, scales = "free", space="free")+ 
  ylab("Number of Crossovers per Cell")+
  geom_point(aes(shape = sex), size=3.7, position=position_dodge(.5))+

  ylim(c(19.5, 33))+
 scale_color_manual(values=colors_of_strains)+ 
  scale_y_continuous(breaks=seq(20,32,2) )+

>>>>

learning that geom_point(position = position_doge(x))
 will shift the two shaped points closer together.  But this isn't the same as the x axis categories being shifted closer together.

So trying to learn how to squish the x axis together
 scale_x_discrete(expand=c(0, 2) ) squishes all the tick marks, but makes a bunch of big space at the boarders

The parameters in expand() -- are connected with the data range. -- expand is used for making padding around the data.  So this might not be the exactly what I am looking for.
It might be that the best way is to make a stand in continous x axis scale for nudging the point positions.

Removing legends, selectively

has to do with which variables are defined within aes(), not sure how to define shape but not color within aes

the color will now be by sex... I could do this in Illustrator

```{r main.plot.code, echo=FALSE, warning=FALSE}
#use the MLH1 / cell level data to calq the error bars
#strain table ggplot

Fig1_Bv2_strain <- ggplot(strain.table.HQ, aes(y=mean_co, x=strain,shape = sex, color=strain),   show.legend = FALSE)+

    geom_point(aes(shape = sex),  size=3.7, position=position_dodge(.29))+

   geom_errorbar(aes(ymin=mean_co-(se*2), ymax=mean_co+(se*2) ), width=.3, position = position_dodge(.29), size=1.001)+

  scale_color_manual(values=colors_of_strains)+

  ylab("Number of Crossovers per Cell")+
  scale_y_continuous(breaks=seq(20,32,2) )+

  scale_x_discrete(expand=c(.08, 0) )+  
  #scale_x_continuous( breaks=c(1,2), limits=c(0,3), expand=c(0,0))+

  theme_classic()+
  theme(legend.position="none",     #legend.position="bottom",legend.box = "horizontal",
        axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank() )+
 #remove all legend for now....

  #  panel.grid.major = element_blank(), panel.grid.minor = #element_blank(),  axis.line=element_line(colour = "black"),
 # panel.background = element_blank()) +

# FINAL DRAFT

put together 3 pieces; plot, cell1, cell2

 todo

   1. finish and import final ai edited polt,

   2. add cell images with cowplot to bottom

```{r load.plots, echo=FALSE}
library(png)
library(ggpubr)

F.first.png <- readPNG('C:/Users/alpeterson7/Documents/MLH1repo/doc/figureFiles/MLH1_F.first.plot_v4.png')
M.first.png <- readPNG('C:/Users/alpeterson7/Documents/MLH1repo/doc/figureFiles/MLH1_M.first.plot_v4.png')

empty.DF <- data.frame(col1 = c(1,3), col2 = c(1,3) )

F.first <- ggplot(empty.DF, aes(x = col1, y = col2)) +
  background_image(F.first.png) + theme(axis.title.x=element_blank(),
                                  axis.text.x=element_blank(),axis.ticks.x=element_blank(),axis.title.y=element_blank(),
                                  axis.text.y=element_blank(),axis.ticks.y=element_blank() )

M.first <- ggplot(empty.DF, aes(x = col1, y = col2)) +
  background_image(M.first.png) + theme(axis.title.x=element_blank(),
                                  axis.text.x=element_blank(),axis.ticks.x=element_blank(),axis.title.y=element_blank(),
                                  axis.text.y=element_blank(),axis.ticks.y=element_blank() )

```{r load.cells, echo=FALSE}

best.oo <- readPNG('C:/Users/alpeterson7/Documents/MLH1repo/doc/figureFiles/cell.images/Best_female_4apr16_17mar16_G_f3_sp1_26_rev.png')
best.spermato <- readPNG('C:/Users/alpeterson7/Documents/MLH1repo/doc/figureFiles/cell.images/Best_male_9mar16_22feb16_G_m1_sp1_15.2_rev.png')

#make empty DF for ggplot object
empty.DF <- data.frame(col1 = c(1,3), col2 = c(1,3) )
#make an empty ggplot thing, then background ontop
spermatocyte.auto <- ggplot(empty.DF, aes(x = col1, y = col2)) +
  background_image(best.spermato) + theme(axis.title.x=element_blank(),
                                  axis.text.x=element_blank(),axis.ticks.x=element_blank(),axis.title.y=element_blank(),
                                  axis.text.y=element_blank(),axis.ticks.y=element_blank() )

oocyte.auto <- ggplot(empty.DF, aes(x = col1, y = col2)) +
  background_image(best.oo) + theme(axis.title.x=element_blank(),
                                  axis.text.x=element_blank(),axis.ticks.x=element_blank(),axis.title.y=element_blank(),
                                  axis.text.y=element_blank(),axis.ticks.y=element_blank() )

# all png loaded in

```{r cow.plot, echo=FALSE}
library("cowplot")

F.first.fig  <- ggdraw() +
  draw_plot(F.first, x = 0, y = .42, width=1, height=.5) +

  draw_plot(spermatocyte.auto, x=.51, y = 0, width=.31, height=.39) +

  draw_plot(oocyte.auto, x=0.01, y = 0, width = .31, height = .39) +

  draw_plot_label(label = c("A", "B", "C"), size = 15,
                  x = c(0, 0, .5), y = c(1, .43, 0.43) )

F.first.fig

#ggsave("~./WildMiceMadison/results/Figure1_32119.png")
```

Loaded slightly nudged points-plot as png. This looks bad, don't do this. Switch to Illustrator.

# redo

```{r redo.plot, echo=FALSE}
redo  <- ggdraw() +

  draw_plot(Fig1_Bv2_strain, x = 0, y = .42, width=1, height=.49) +

  draw_plot(spermatocyte.auto, x=.55, y = 0, width=.4, height=.41) +

  draw_plot(oocyte.auto, x=0.05, y = 0, width = .4, height = .41) +

  draw_plot_label(label = c("A", "B", "C"), size = 15,
                  x = c(0, 0, .5), y = c(1, .43, 0.43) )

redo
```

All pieces are 'made' within R. But I can't figure out how to reduce the x axis white space between points (strains). The message boards seem to indicate that using a continous_x scale might be the only way to get the layout I want.

@@
